Bee brain size is positively associated with urban lifestyles but not with positive population trends

### 2022-11-21 Manuscript/Ms.Rmd
edits

#Script to load variables
library(readr)
library(dplyr)

raw = read_csv("../Raw_data/all_cleaning.csv")

@@

@@

Our dataset consist in bee specimens captured by hand netting in different areas of the East Coast of the United States and Europe (i.e., Spain and Netherlands). In total, it contains `r sum(d$individuals)` female individuals from `r nlevels(factor(unique(d$Species)))` species with brain weight and body size information. Of these, 93 species with their respective traits were previously published in @sayol2020. We considered exclusively female individuals as most bees exhibit sexual dimorphism [@shreeves2008] that likely imply intraspecific differences in brain size between male and female individuals.

>>>>

library(readr)
library(dplyr)

#Load final dataset 
raw = read_csv("../Raw_data/all_cleaning.csv")

@@

#Load taxonomic rank script
tax = read_csv("../Data/Processing/taxonomic_rank.csv")

@@

Our dataset contains measurements of brain weight and body size for bee specimens captured by hand netting in different areas of the East Coast of United States and Europe (i.e., Spain and Netherlands). In total, the dataset includes `r sum(d$individuals)` female individuals from `r nlevels(factor(unique(d$Species)))` species that represent `r nlevels(factor(unique(tax$family)))` families and `r nlevels(factor(unique(tax$genus)))` genera. We have considered exclusively female specimens as most bees exhibit sexual dimorphism [@shreeves2008] that likely imply intraspecific differences in brain size between male and female individuals.
